Holomorphic field theories and higher algebra

### 2025-01-29 draft.tex
finished with refs

Derived geometry is a sophisticated subject but the motivations and first steps are surprisingly simple,
as we now attempt to explain.
In this paper we only need the reader to understand the rough outline of derived geometry to follow our discussion,
but there are several, much more substantial expositions now available.
(For algebraic geometers consider \cite{Toen,PridEug}; for symplectic or Poisson geometers consider \cite{PTVV, Safronov}; for differential geometers consider \cite{Joyce}; and for representation theorists consider \cite{BZNad, GaiRoz, Raskin}.)

>>>>

Derived geometry is a sophisticated subject but the motivations and first steps are surprisingly simple,
as we now attempt to explain.
In this paper we only need the reader to understand the rough outline of derived geometry to follow our discussion,
but there are several, much more substantial expositions now available.
(For algebraic geometers consider \cite{Toen,PridEug}; for symplectic or Poisson geometers consider \cite{PTVV, Safronov}; for differential geometers consider \cite{Joyce}; and for representation theorists consider \cite{GaiRoz}.)
